Untitled

### 2021-01-06 ms/manuscript.Rmd
Add captions using captioner

Ability to recover from desiccation was tested in sporophytes of `r n_dt_species_sporo` species and gametophytes of `r n_dt_species_gameto` species, including `r n_dt_species_both` species with both life phases (Appendix S3).
A general correlation of DT with habitat was observed in sporophytes (Fig. 4).
Both terrestrial species (*Abrodictyum dentatum* (Bosch) Ebihara & K Iwats. and *C. apiifolia*) lacked even moderate DT, and failed to recover from the gentlest treatment of 2 d at --38 MPa (more stringent tests were not conducted on these species after confirming their lack of DT at this level).
Saxicolous species (*Crepidomanes kurzii* (Bedd.) Tagawa & K. Iwats., *Polyphlebium endlicherianum* (C. Presl) Ebihara & K. Iwats., and *Vandenboschia maxima* (Blume) Copel.) also had low DT; only *C. kurzii* was able to recover from desiccation up to --86 MPa for 2 d but not more.
All epiphytic species were capable of recovering from desiccation to a certain degree, but ability varied between species.
Most low elevation epiphytes could not tolerate long periods (15 d) of desiccation; only *Crepidomanes bipunctatum* (Poir.) Copel. was able to recover from desiccation longer than 2 d.
Most of the high elevation epiphytes could recover from 2 d treatments regardless of desiccation intensity (except for *H.* *pallidum* and *P.* *borbonicum*, which failed to recover from 2 d at --282 MPa), and many could withstand desiccation for 15 d.
Interestingly, *C. minutum* var. 2, *Hymenophyllum multifidum* (G. Forst.) Sw., and *Hymenophyllum polyanthos* (Sw.) Sw. could recover from desiccation at --86 or --282 MPa for 15 d, but not --38 MPa.

@@

Acknowledgments

@@

## Figure Captions

**Fig. 1** Results of sporophyte desiccation tolerance test on filmy fern sporophytes from Moorea, French Polynesia.
Recovery was measured by comparing maximum photochemical yield of photosystem II before desiccation treatment with values at 30 min, 24 hr, and 48 hr following desiccation at three different intensities for either 2 or 15 days (see Methods).
Recovery was not measured for all combinations of species and desiccation treatments; missing points indicate data not collected (not recovery of 0%).
Error bars indicate standard deviation.
Growth habit indicated in parentheses after each species: T, terrestrial; S, saxicolous; LE, low elevation epiphyte; HE, high elevation epiphyte

@@

**Fig. 1**

>>>>

Ability to recover from desiccation was tested in sporophytes of `r n_dt_species_sporo` species and gametophytes of `r n_dt_species_gameto` species, including `r n_dt_species_both` species with both life phases (Appendix S3).
A general correlation of DT with habitat was observed in sporophytes (`r figure("sporo-dt")`).
Both terrestrial species (*Abrodictyum dentatum* (Bosch) Ebihara & K Iwats. and *C. apiifolia*) lacked even moderate DT, and failed to recover from the gentlest treatment of 2 d at --38 MPa (more stringent tests were not conducted on these species after confirming their lack of DT at this level).
Saxicolous species (*Crepidomanes kurzii* (Bedd.) Tagawa & K. Iwats., *Polyphlebium endlicherianum* (C. Presl) Ebihara & K. Iwats., and *Vandenboschia maxima* (Blume) Copel.) also had low DT; only *C. kurzii* was able to recover from desiccation up to --86 MPa for 2 d but not more.
All epiphytic species were capable of recovering from desiccation to a certain degree, but ability varied between species.
Most low elevation epiphytes could not tolerate long periods (15 d) of desiccation; only *Crepidomanes bipunctatum* (Poir.) Copel. was able to recover from desiccation longer than 2 d.
Most of the high elevation epiphytes could recover from 2 d treatments regardless of desiccation intensity (except for *H.* *pallidum* and *P.* *borbonicum*, which failed to recover from 2 d at --282 MPa), and many could withstand desiccation for 15 d.
Interestingly, *C. minutum* var. 2, *Hymenophyllum multifidum* (G. Forst.) Sw., and *Hymenophyllum polyanthos* (Sw.) Sw. could recover from desiccation at --86 or --282 MPa for 15 d, but not --38 MPa.

@@

**Acknowledgments**

@@

## Figure Captions
<!-- JPR requirements: Figure captions begin with the term Fig. in bold type, followed by the figure number, also in boldtype. No punctuation is to be included after the number, nor is any punctuation to be placed at the end of the caption. -->

**`r figure("sporo-dt")`** Results of sporophyte desiccation tolerance test on filmy fern sporophytes from Moorea, French Polynesia.
Recovery was measured by comparing maximum photochemical yield of photosystem II before desiccation treatment with values at 30 min, 24 hr, and 48 hr following desiccation at three different intensities for either 2 or 15 days (see Methods).
Recovery was not measured for all combinations of species and desiccation treatments; missing points indicate data not collected (not recovery of 0%).
Error bars indicate standard deviation.
Growth habit indicated in parentheses after each species: T, terrestrial; S, saxicolous; LE, low elevation epiphyte; HE, high elevation epiphyte

@@

**`r figure("sporo-dt")`**
